Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Spanserver Software Stack

Each spanserver also consists of multiple software layers (four at least). At the
bottom layer, every spanserver is responsible for between 100 and 1,000
\emph{tablets}. A tablet is bag of key-value mappings of the form
\begin{center}
  \texttt{(key:string, timestamp:int64)} $\rightarrow$ \texttt{value}
\end{center}
This is somehow similar to the tablet abstraction used in Bigtable. However,
Spanner \emph{automatically} assigns timestamps to data which makes Spanner a
\emph{multi-version} database. The state of a tablet is stored on a distributed
file system called \emph{Colossus}, the successor of the Google File
System~\cite{Ghemawat:2003}.

On top of each tablet, a Paxos state machine is implemented in order to support
consistent replication. One Paxos state machine is elect as leader. Leases are
assigned in a long-lived manner (default lease length is 10 seconds). A leader
implements three additional layers. A \emph{lock table} which stores the state
for two-phase locking and therefore implements the concurrency control. On top
of the lock table, a \emph{transaction manager} is implemented to coordinate
distributed transactions. In turn, this transaction manager is used to implement
a \emph{participant leader}. This leader is only utilized if a transaction
involves multiple Paxos groups (set of replicas). In this case, one of the
participant groups is chosen as coordinator and the leader of this group is
referred to as \emph{coordinator leader}.
Figure~\ref{subfig:spanserver-software-stack} shows the spanserver software stack
as described before.

>>>>

Each spanserver again consists of multiple software layers (four at least). At
the bottom layer, every spanserver is responsible for between 100 and 1,000
\emph{tablets}. A tablet is bag of key-value mappings of the form
\begin{center}
  \texttt{(key:string, timestamp:int64)} $\rightarrow$ \texttt{value}
\end{center}
This is somehow similar to the tablet abstraction used in Bigtable. However,
Spanner \emph{automatically} assigns timestamps to data which makes Spanner a
\emph{multi-version} database. The state of a tablet is stored on a distributed
file system called \emph{Colossus}, the successor of the Google File
System~\cite{Ghemawat:2003}.

On top of each tablet, a Paxos state machine is implemented in order to support
consistent replication. One Paxos state machine is elect as leader. Leader leases
are assigned in a long-lived manner (default lease length is 10 seconds). A leader
implements three additional layers. A \emph{lock table} which stores the state
for two-phase locking and therefore implements the concurrency control. On top
of the lock table, a \emph{transaction manager} is implemented to coordinate
distributed transactions. In turn, this transaction manager is used to implement
a \emph{participant leader}. This leader is only utilized if a transaction
involves multiple Paxos groups (set of replicas). In this case, one of the
participant groups is chosen as coordinator and the leader of this group is
referred to as \emph{coordinator leader}.
Figure~\ref{subfig:spanserver-software-stack} shows the spanserver software stack.
